|

### 2021-02-22 manuscript/article.Rmd

---
title:  |
        | Financial Incentives and Health Care Provision: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
author: 
  - Danilo Freire[^freire]
  - Umberto Mignozzetti[^mignozzetti]
date: \today
thanks: "We thank Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Guisela Pereira, Adam Przeworski, Catarina Roman, David Skarbek, Denis Stukal, Marcos Tourinho, Scott Tyson, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments. Special thanks to XXXX for their excellent research assistance. Replication materials are available at <http://github.com/danilofreire/incentives-health-care>."
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: unsrtnat
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: template.latex
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)
# Install required packages
pkgs <- c('tidyverse', 'magrittr', 'lmtest',
          'estimatr', 'sandwich', 'stargazer',
          'gridExtra', 'WeightIt', 'robustHD', 
          'kableExtra', 'lfe')

@@

\noindent \textbf{Background}. Mosquito control strategies are the primary
means to reduce \textit{Aedes aegypti} infections worldwide. However,
insecticide spraying is conducted inconsistently across the developing world.
Recent studies indicate that financial incentives may increase the productivity
of health personnel, yet there is little evidence on the impact of monetary
rewards on \textit{A. aegypti}-reduction programmes. We evaluated whether
individual and collective financial incentives improves the performance of
healthcare workers fighting \textit{A. aegypti}, as well as their effect on
city-level numbers of dengue hospitalisations.

\noindent \textbf{Methodology/Principal findings}. We hired and trained
subjects to visit households, find \textit{A. aegypti} breeding sites, and kill
mosquito larvae in the city of Rio Verde, Brazil. In our randomised field
trial, we provided individual and team bonuses to two treatment groups, while
the control group received a flat compensation for completing their tasks.
Financial bonuses increased the number of cleaned breeding sites in both
treatment groups (individual and team bonuses) and the collective treatment
also improved larvae extermination. The intervention lowered dengue
hospitalisations in 10.3\%, but the result was not consistent across all model
specifications.

@@

\noindent Diseases transmitted by the \textit{Aedes aegypti} mosquito, such as
chikungunya, dengue, yellow fever, and Zika, continue to kill thousands of
people per year. As there are no safe vaccines for many of these infections,
insecticide spraying and breeding site cleaning are the best means to fight the
mosquito. In several developing countries, which host the majority of
\textit{A. aegypti} infections, anti-mosquito campaigns are carried out
inconsistently, thus it is crucial to find ways to improve the productivity of
healthcare workers in charge of these tasks. We designed a randomised field
experiment that provided individual and collective financial incentives to
healthcare agents in a Brazilian city and tested the effect of monetary rewards
on their productivity and on the number of dengue hospitalisations. We find
that financial bonuses improved the number of cleaned breeding sites in both
treatment groups (individual and team incentives) and that the collective
treatment also improved larvae extermination. The impact of our treatment on
city-level hospitalisations was not consistent across all specifications. In
sum, financial incentives may be used to boost field productivity in
anti-\textit{A. aegypti} programmes, but we suggest that further research is
required to evaluate how healthcare worker productivy impacts city-level
disease outcomes.

\vspace{.3cm}
\noindent \textbf{Keywords}: Aedes aegypti, dengue, financial incentives, mosquito control, preventive health care, randomised field experiment, worker productivity
\end{abstract}

@@

\newpage
# Introduction
\label{sec:intro}

The *Aedes aegypti* mosquito is the major worldwide vector of several arboviral
diseases, including dengue, yellow fever, Zika, and chikungunya
[@burt2012chikungunya; @jansen2010dengue; @leta2018global;
@thangamani2016vertical]. Over the past 30 years, arboviral incidence has
increased exponentially, with estimates suggesting that dengue is endemic in
around 100 countries and causes 400 million infections and 22 thousands deaths
each year [@bhatt2013global; @cdc2020dengue]. Since there are no safe vaccines
for most *Aedes*-transmitted diseases [@world2017dengue], we have seen a number
of dengue and Zika outbreaks in Asia, the Caribbean, South America, and the
United States [@carlson2016ecological; @leta2018global]. Chikungunya virus,
previously endemic only to Africa, has already been reported in every region of
the world [@grandadam2011chikungunya; @kraemer2015global; @mayer2017emergence].

Mosquito control is the primary strategy to prevent *Aedes*-borne infections
[@beatty2010best; @eisen2009proactive]. The World Health Organization
recommends the elimination of containers and the use of insecticide to reduce
vector breeding, specially in settings where human-vector contacts are
frequent, such as schools, hospitals, and workplaces [@WHO2012global;
@world2020denguecontrol]. However, breeding site cleaning and insecticide
spraying are labour-intensive processes, and they are often carried out
inconsistently in developing countries [@paz2015dengue; @siddiqui2016use;
@WHO2012global]. In this regard, improving the performance of those responsible
for mosquito control is essential to the effectiveness of anti-*Aedes*
programmes.

Research shows that financial incentives may increase the productivity of
health care workers [@clemens2014physicians; @muthmainnah2017improving;
@ulrich2005does]. Nevertheless, systematic reviews indicate that the
generalisability of the available evidence is limited due to methodological
shortcomings, as several studies suffer from selection bias and inadequate
experimental blinding [@bassani2013financial; @flodgren2011overview;
@scott2011effect]. Moreover, it remains unclear which rewarding schemes have a
stronger effect on health care worker performance [@fainman2020design], and
whether monetary incentives have a sustained effect on patient outcomes
[@jha2012long; @langdown2014use].

In this paper, we explore how financial incentives affect the productivity of
health care personnel involved in *A. aegypti* control and how they impact
dengue hospitalisations. We run a randomised field experiment in the city of
Rio Verde, Brazil, which has experienced a peak in dengue infections in the
last years. We hired and trained teams of health care workers to perform
simplified procedures designed to exterminate *A. aegypti* breeding sites. Our
experiment consisted of two treatment arms plus a control condition. We offered
individual or collective bonuses to those allocated in the two treatment
groups, while the control group received a fixed compensation for completing
their tasks. We then measured how the different reward schemes affect the
number of breeding sites discovered, larvae exterminated, and city-level dengue
incidence.

@@

We conducted a randomised field trial in Rio Verde, a municipality in the
Brazilian Midwestern state of Goiás. In 2017, Rio Verde had 229,000 inhabitants
and 1,156 confirmed dengue cases, one of highest counts in Goiás
[@goias2020]. We used Facebook advertisements to recruit potential
participants. The advertisements directed applicants to Google Forms, where we
asked for their contact information. We sent a pre-treatment demographic survey
to every applicant who provided a valid email address. At this stage, we
excluded all individuals under 18 years old and invited the remaining
applicants to our training session, which we ran on the 4^th^ of May, 2018. The
meeting involved a lecture on *A. aegypti* vector biology and practical
instructions on how to find and exterminate mosquito breeding sites. Those who
did not attend the session were also excluded from the study.

Table \ref{tab:covbal} displays the attrition and covariate balance tests for
our experiment, and the territorial assignment before and after applying
propensity score matching [@rosenbaum1985constructing] on census tract
characteristics. We observe no significant differences regarding attrition
rates, indicating that the treatment was correctly randomised. Participant 
demographics are also similar across all groups, thus the matching technique
successfully balanced the territorial assignment.

@@

# N
x = round(tapply(rep(1, length(aux$assign3)), 
                 aux$assign3,
                 sum), digits = 0)
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
for (i in 1:dim(tabcov)[1]) {
  s <- paste(tabcov[i,], collapse = ' & ')
  s <- gsub('NA', '', paste(tabcov[i,], collapse = ' & '))
  cat(paste(s, ' \\\\ ', sep = ''), '\n')
}
```
\hline \\[-1.8ex] 
& \multicolumn{5}{l}{Panel C: Unmatched Covariate Balance on Territorial Assignment} \\
\hline \\[-1.8ex] 
```{r, echo = FALSE, cache=TRUE, results='asis'}
## Census Sectors characteristics
tabcov <- data.frame()

@@

dfr$weightsD2 <- weightit(D2~NHouses+
                            NHouseholds+AvgHouseholdSize+
                            logAvgIncomeHousehold+plac, 
                          data = dfr, focal = "No intervention", 
                          method = 'cbps',
                          estimand = "ATT")$weights
for (i in 1:dim(tabcov)[1]) {
  s <- paste(tabcov[i,], collapse = ' & ')
  s <- gsub('NA', '', paste(tabcov[i,], collapse = ' & '))
  cat(paste(s, ' \\\\ ', sep = ''), '\n')
}
```
\hline \\[-1.8ex] 
& \multicolumn{5}{l}{Panel D: Matched Covariate Balance on Territorial Assignment} \\
\hline \\[-1.8ex] 
```{r, echo = FALSE, cache=TRUE, results='asis'}
tabcov <- data.frame()
# Number of Houses
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(NHouses, weightsD1),
            .groups = 'drop')
x = x$x
x
y = summary(aov(NHouses~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Number of Houses',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

@@

The intervention took place on the 5^th^ of May, 2018. We randomly assigned
subjects into three groups and directed each group to separate headquarters to
avoid spillovers. In the control group (n = `r as.numeric(table(prodfr$D)[1])`), we told participants that
they would receive a flat payment regardless of their performance (BRL 110 /
USD 25 per subject). In the individual treatment group (n = `r as.numeric(table(prodfr$D)[2])`), we informed
subjects that we would rank each subject separately and double the compensation
for those who performed above the sample median (BRL 220 / USD 50 per subject).
In the collective treatment group (n = `r as.numeric(table(prodfr$D)[3])`), we explained that we would rank
the performance of each group and double the payment for those teams whose
results were higher than the sample median (BRL 220 / USD 50 per subject).
Participants worked in pairs and were aware of other groups, but they did not
know about the different treatment conditions. The teams received a leaflet
with a map of the area they should cover. Each route included around 120 houses
in two or three blocks.

@@

This study evaluates two outcomes. The first outcome is the field productivity
of health care providers. We measure worker productivity by coding cellphone
data collected during the intervention into four indicators: 1) the number of
houses visited; 2) the number of houses visited within less than two minutes;
3) the number of breeding sites removed and cleaned; 4) the number of
exterminated larvae. We analyse the data using ordinary least squares with
robust standard errors [@imbens2016robust]. We estimate the statistical
power of the study assuming a treatment effect of 0.15 standard deviations.

The second outcome of interest is dengue incidence in the municipality of Rio
Verde measured 4, 8, 12, and 16 days after the intervention. The Rio Verde
Mayor's Office provided us with its annual health care report, which contains
the dates and personal information of patients who had dengue fever and
received hospital treatment from January to September 2018. We georeferenced
the home addresses of the patients and compared the incidence map with the
distribution of our intervention. We also compare dengue incidence in each of
the treatment statuses with incidence figures in the control group. In both
models, the unit of analysis is the census tract. We employ a
differences-in-differences estimator to measure the treatment effects
[@angrist2008mostly].

We pre-registered the experiment on the Evidence in Governance and Policy
(EGAP) website (<https://osf.io/6q8vu/>), and received IRB approval from New
York University (IRB-FY2017-17) and Fundação Getulio Vargas (IRB-01/2017). The
funders of this study had no influence over the formulation, organisation,
analysis, and interpretation of the outcomes. Health care workers gave written
consent upon filling the Qualtrics questionnaire. During the intervention, the
occupants of households inspected for breeding sites and larvae gave oral
consent. For more information on the experimental design, sample
characteristics, exclusion criteria, and estimation methods, please refer to
the Supplementary Material.

@@

We find that financial incentives significantly increase the field productivity
of health care workers fighting *Aedes aegypti*. Subjects in both the
individual and the collective bonus groups locate more mosquito breeding sites
and exterminate more larvae than participants in the control condition. Our
results also show the intervention decreases city-wide levels of dengue
incidence, but the coefficients only reach statistical significance when we
combine the two treatments and contrast them with the control group. Overall,
the findings suggest that monetary payments are an effective method of
improving health worker performance, yet more research is needed to assess
whether higher labour productivity leads to fewer dengue-related
hospitalisations.

@@

We have four indicators to measure health worker productivity. The first is the
number of houses visited during the intervention. The second indicator is the
number of houses in which the visits lasted for less than two minutes. The
third dependent variable is the number of *A. aegypti* breeding sites removed
and cleaned. Our fourth variable indicates the number of mosquito larvae
exterminated. Table \ref{tab:productivity} summarises the experimental results.

```{r, echo = FALSE, results='asis', warning=FALSE}
## Productivity outcome
mprod <- list()
mprod[[1]] <- lm(nHouse ~ D, data = prodfr)
mprod[[2]] <- lm(nHouseLessTwoMin ~ D, data = prodfr)
mprod[[3]] <- lm(nBreed ~ D, data = prodfr)
mprod[[4]] <- lm(nLarvae ~ D, data = prodfr)
stargazer(mprod[[1]], mprod[[2]],
          mprod[[3]], mprod[[4]],
          se = starprep(mprod[[1]], mprod[[2]],
                        mprod[[3]], mprod[[4]],
                        se_type = "HC1"),
          dep.var.labels = c('\\shortstack{Houses \\\\ Visited}', 
                             '\\shortstack{Houses Visited \\\\ in Less than \\\\ Two Minutes}',
                             '\\shortstack{Breeding Sites \\\\ Terminated}',
                             '\\shortstack{Larvae \\\\ Terminated}'),
          keep.stat = c('ser', 'n'),
          notes = c('Robust Standard Errors in parenthesis.'),
          keep = c('DIndividual', 'DCollective'),
          covariate.labels = c('Individual Bonus',
                               'Collective Bonus'),
          title = 'Field Productivity', header = FALSE,
          label = 'tab:productivity')
```

Subjects who received monetary incentives, either alone or in pairs, visited
fewer houses than those who did not earn financial rewards. While the result
seems counter-intuitive, it actually attests the effectiveness of the
treatment. This is because we offered incentives for subjects to exterminate
larvae and find breeding sites, not to visit a greater number of households. As
a result, participants in the two treatment groups did a thorough job in each
household, which explains the lower number of visits during the allotted time.
We find that subjects in the individual and in the collective bonus groups
visited `r round(as.numeric(coef(mprod[[1]])[2]), 3)` (CI: [`r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[2,1]`, `r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[2,2]`]) and `r round(as.numeric(coef(mprod[[1]])[3]), 3)` (CI: [`r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[3,2]`]) households,
respectively.

Our second indicator provides further evidence in favour of our argument. We
see that the two groups which earned performance bonuses spent more time in the
households, as their number of houses visited for less than two minutes is
significantly lower than those of the control condition. On average,
participants in the individual bonus treatment arm visited `r round(as.numeric(coef(mprod[[2]])[2]), 3)` (CI: [`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[2,1]`,
`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[2,2]`]) houses than the control, and those in the collective bonus group visited
`r round(as.numeric(coef(mprod[[2]])[3]), 3)` (CI: [`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[3,2]`]).

Incentivised teams find and clean more breeding sites than non-incentivised
ones. Individually incentivised health workers find `r round(as.numeric(coef(mprod[[3]])[2]), 3)` (CI: [`r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[2,1]`, `r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[2,2]`])
more breeding sites than the non-incentivised control group. The effect for
those in the collective bonus group is `r round(as.numeric(coef(mprod[[3]])[3]), 3)` (CI: [`r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[3,2]`]), slightly
smaller than for the individual treatment.

>>>>

---
title:  |
        | Financial Incentives and Healthcare Provision: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
author:
  - Danilo Freire[^freire]
  - Umberto Mignozzetti[^mignozzetti]
date: \today
thanks: "We thank Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Guisela Pereira, Adam Przeworski, Catarina Roman, David Skarbek, Denis Stukal, Marcos Tourinho, Scott Tyson, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments. Replication materials are available at <http://github.com/danilofreire/incentives-health-care>."
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: unsrtnat
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: template.latex
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)

# Install required packages
pkgs <- c("tidyverse", "magrittr", "lmtest",
          "estimatr", "sandwich", "stargazer",
          "gridExtra", "WeightIt", "robustHD",
          "kableExtra", "lfe", "fixest")

@@

\noindent \textbf{Background}. Mosquito control is the most effective means of
reducing \textit{Aedes aegypti} infections worldwide. In many developing
countries, however, vector management programmes fail to reach their goals due
to low worker productivity. Research suggests that financial incentives may
increase the productivity of health personnel, yet there is little evidence
about the impact of monetary rewards on \textit{A. aegypti}-reduction
strategies. We evaluated whether individual and collective financial incentives
improve the performance of healthcare workers fighting \textit{A. aegypti}, as
well as their effect on city-level numbers of dengue hospitalisations.

\noindent \textbf{Methodology/Principal findings}. We hired and trained
subjects to visit households, find \textit{A. aegypti} breeding sites, and
eliminate mosquito larvae in the city of Rio Verde, Brazil. We randomly
assigned workers into three groups. The control group received a flat
compensation for their tasks, while workers in the two treatment groups received
individual and collective monetary bonuses, respectively. Financial rewards
increased the number of cleaned breeding sites in both treatment groups
(individual and team bonuses) and the collective treatment also improved larvae
extermination. The intervention lowered dengue hospitalisations in 10.3\%, but
the result was not consistent across all model specifications.

@@

\noindent Diseases transmitted by the \textit{Aedes aegypti} mosquito, such as
chikungunya, dengue, yellow fever, and Zika, continue to affect thousands of
people per year. As there are no safe vaccines for most of these infections,
insecticide spraying and breeding site elimination are the best means to fight
the mosquito. In several developing countries, which host the majority of
\textit{A. aegypti} infections, anti-mosquito campaigns are carried out
inconsistently, thus it is crucial to find ways to improve the productivity of
healthcare workers in charge of these tasks. We designed a randomised field
experiment that provided individual and collective financial incentives to
healthcare agents in a Brazilian city, and we tested the effect of monetary
rewards on their productivity and on city-level dengue hospitalisations. We
find that financial bonuses improved the number of cleaned breeding sites in
both treatment groups (individual and team incentives) and that the collective
treatment also improved larvae extermination. The impact of our treatment on
city-level hospitalisations was not consistent across all specifications. In
sum, financial incentives may be used to boost field productivity in
anti-\textit{A. aegypti} programmes, but further research is required to
evaluate how healthcare worker productivy impacts dengue outcomes.

\vspace{.3cm} 
\noindent \textbf{Keywords}: Aedes aegypti, dengue, financial
incentives, mosquito control, preventive healthcare, randomised field
experiment, worker productivity 
\end{abstract}

@@

# Introduction
\label{sec:intro}

The *Aedes aegypti* mosquito is the major worldwide vector of several arboviral
diseases, including chikungunya, dengue, yellow fever, and Zika
[@burt2012chikungunya; @jansen2010dengue; @leta2018global;
@thangamani2016vertical]. Over the last decades, arboviral incidence has
increased exponentially, with estimates suggesting that dengue is endemic in
over 100 countries and causes 400 million infections and 22 thousand deaths
each year [@bhatt2013global; @cdc2020dengue]. Since there are no safe vaccines
for most *Aedes*-transmitted diseases [@world2017dengue], we have seen a number
of dengue and Zika outbreaks in Asia, the Caribbean, South America, and the
United States [@carlson2016ecological; @leta2018global]. Chikungunya virus,
previously endemic only to Africa, has already been reported in every region of
the world [@grandadam2011chikungunya; @kraemer2015global; @mayer2017emergence].

Mosquito control is the primary strategy to prevent *Aedes*-borne infections
[@beatty2010best; @eisen2009proactive]. The World Health Organization
recommends the cleaning of containers and the use of insecticide to reduce
vector breeding, specially in settings where human-vector contacts are
frequent, such as schools, hospitals, and workplaces [@WHO2012global;
@world2020denguecontrol]. However, breeding site elimination and insecticide
spraying are labour-intensive processes, which are often carried out
inconsistently by developing states [@paz2015dengue; @siddiqui2016use;
@WHO2012global]. In this regard, improving their health agency's performance in
mosquito control is essential to the effectiveness of anti-*Aedes* programmes.

Research shows that financial incentives may increase the productivity of
healthcare workers [@clemens2014physicians; @muthmainnah2017improving;
@ulrich2005does]. Nevertheless, systematic reviews indicate that the internal
validity of the available evidence is limited due to methodological
shortcomings, as several studies suffer from selection bias and inadequate
experimental blinding [@bassani2013financial; @flodgren2011overview;
@scott2011effect]. The reviews also point out that it remains unclear which
rewarding schemes have a stronger impact on healthcare worker performance
[@fainman2020design] and whether monetary incentives have any sustained effects
on patient outcomes [@jha2012long; @langdown2014use].

In this paper, we explore how financial incentives affect the productivity of
healthcare personnel involved in *A. aegypti* control and how they impact
dengue hospitalisations. We ran a randomised field experiment in the city of
Rio Verde, Brazil, which has experienced a peak in dengue infections in recent
years. We hired and trained teams of healthcare workers to perform simplified
procedures designed to exterminate *A. aegypti* breeding sites. Our experiment
consisted of two treatment arms plus a control condition. We offered individual
or collective bonuses to those allocated in the two treatment groups, while the
control group received a fixed compensation for completing their tasks. We then
measured how the different reward schemes affected the number of breeding sites
discovered, larvae exterminated, and city-level numbers of dengue incidence.

@@

We conducted a randomised field trial in Rio Verde, a municipality in the
Brazilian Midwestern state of Goiás. In 2017, Rio Verde had 229,000 inhabitants
and 1,156 confirmed dengue cases, one of highest counts in the state
[@goias2020]. We used Facebook advertisements to recruit potential
participants. The advertisements directed applicants to Google Forms, where we
asked for their contact information. We sent a pre-treatment demographic survey
to every applicant who provided a valid email address. At this stage, we
excluded all individuals under 18 years old and invited the remaining
applicants to our training session, which we ran on the 4^th^ of May, 2018. The
meeting involved a lecture on *A. aegypti* vector biology and practical
instructions on how to find and exterminate mosquito breeding sites. Those who
did not attend the session were also excluded from the study.

Table \ref{tab:covbal} displays the attrition rates and the covariance balance
tests for our experiment. The last two tables report the values for our
territorial assignment before and after applying propensity score matching
[@rosenbaum1985constructing] on census tract characteristics. We observe no
significant differences regarding attrition rates, indicating that the
treatment was correctly randomised. Participant demographics are also similar
across all groups, what suggests that the matching technique successfully
balanced the territorial assignment.

@@

# N
x = round(tapply(rep(1, length(aux$assign3)),
                 aux$assign3,
                 sum), digits = 0)
row.names(tabcov) <- NULL
for (i in 1:dim(tabcov)[1]) {
  s <- paste(tabcov[i,], collapse = ' & ')
  s <- gsub('NA', '', paste(tabcov[i,], collapse = ' & '))
  cat(paste(s, ' \\\\ ', sep = ''), '\n')
}
```
\hline \\[-1.8ex]
& \multicolumn{5}{l}{Panel C: Unmatched Covariate Balance on Territorial Assignment} \\
\hline \\[-1.8ex]
```{r, echo = FALSE, cache=TRUE, results='asis'}
## Census Sectors characteristics
tabcov <- data.frame()

@@

dfr$weightsD2 <- weightit(D2~NHouses+
                            NHouseholds+AvgHouseholdSize+
                            logAvgIncomeHousehold+plac,
                          data = dfr, focal = "No intervention",
                          method = 'cbps',
                          estimand = "ATT")$weights
for (i in 1:dim(tabcov)[1]) {
  s <- paste(tabcov[i,], collapse = ' & ')
  s <- gsub('NA', '', paste(tabcov[i,], collapse = ' & '))
  cat(paste(s, ' \\\\ ', sep = ''), '\n')
}
```
\hline \\[-1.8ex]
& \multicolumn{5}{l}{Panel D: Matched Covariate Balance on Territorial Assignment} \\
\hline \\[-1.8ex]
```{r, echo = FALSE, cache=TRUE, results='asis'}
tabcov <- data.frame()
# Number of Houses
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(NHouses, weightsD1),
            .groups = 'drop')
x = x$x
y = summary(aov(NHouses~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Number of Houses',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

@@

The intervention took place on the 5^th^ of May, 2018. We randomly assigned
subjects into three groups and directed each group to separate headquarters to
avoid spillovers. In the control group (n = `r as.numeric(table(prodfr$D)[1])`),
we told participants that they would receive a flat payment regardless of their
performance (BRL 110 / USD 25 per subject). In the individual treatment group
(n = `r as.numeric(table(prodfr$D)[2])`), we informed participants that we would
rank each one of them separately and double the compensation for those who
performed above the sample median (BRL 220 / USD 50 per subject). In the
collective treatment group (n = `r as.numeric(table(prodfr$D)[3])`), we
explained that we would rank the performance of each group and double the
payment for those teams whose results were higher than the sample median (BRL
220 / USD 50 per subject). Participants worked in pairs and were aware of other
groups, but they did not know about the different treatment conditions. The
teams received a leaflet with a map of the area they should cover. Each route
included around 120 houses in two or three blocks.

@@

This study evaluates two outcomes. The first outcome is the field productivity
of healthcare providers. We measure worker productivity by coding cellphone
data collected during the intervention into four indicators: 1) the number of
breeding sites removed and cleaned; 2) the number of exterminated larvae; 3)
the number of houses visited; 4) the number of houses visited within less than
two minutes. We analyse the data using ordinary least squares with robust
standard errors [@imbens2016robust]. We estimate the statistical power of the
study assuming a treatment effect of 0.15 standard deviations.

The second outcome of interest is dengue incidence in the municipality of Rio
Verde measured 4, 8, 12, and 16 days after the intervention. The Rio Verde
Mayor's Office provided us with its annual healthcare report, which contains
the dates and personal information of patients who had dengue fever and
received hospital treatment from January to September 2018. We georeferenced
the home addresses of the patients and compared the incidence map with the
distribution of our intervention. We also compare dengue incidence in each of
the treatment statuses with incidence figures in the control group. In both
models, the unit of analysis is the census tract. We employ a
differences-in-differences estimator to measure the treatment effects
[@angrist2008mostly].

We pre-registered the experiment on the Evidence in Governance and Policy
(EGAP) website (<https://osf.io/6q8vu/>), and received IRB approval from New
York University (IRB-FY2017-17) and Fundação Getulio Vargas (IRB-01/2017). The
funders of this study had no influence over the formulation, organisation,
analysis, and interpretation of the outcomes. Healthcare workers gave written
consent upon filling the Qualtrics questionnaire. During the intervention, the
occupants of households inspected for breeding sites and larvae gave oral
consent. For more information on the experimental design, sample
characteristics, exclusion criteria, and estimation methods, please refer to
the Supplementary Material.

@@

We find that financial incentives significantly increase the field productivity
of healthcare workers fighting *Aedes aegypti*. Subjects in both the
individual and the collective bonus groups locate more mosquito breeding sites
and exterminate more larvae than participants in the control condition. Our
results also show the intervention decreases city-wide levels of dengue
incidence, but the coefficients only reach statistical significance when we
combine the two treatments and contrast them with the control group. Overall,
the findings suggest that monetary payments are an effective method of
improving health worker performance, yet more research is needed to assess
whether higher labour productivity leads to fewer dengue-related
hospitalisations.

@@

Table \ref{tab:productivity} summarises the experimental results. 
Subjects who receive monetary incentives find and clean more breeding sites
than those who earned a flat compensation fee. Workers in the individual
treatment group find `r round(as.numeric(coef(mprod[[3]])[2]), 3)` (CI: [`r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[2,1]`, `r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[2,2]`]) more breeding sites than the
non-incentivised control group. The effect for those in the collective bonus
group is `r round(as.numeric(coef(mprod[[3]])[3]), 3)` (CI: [`r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[3,2]`]), slightly smaller than for the individual treatment. This finding suggests that the treatment does improve the performance of healthcare workers.

```{r, echo = FALSE, results='asis', warning=FALSE}
## Productivity outcome
mprod <- list()
mprod[[1]] <- lm(nHouse ~ D, data = prodfr)
mprod[[2]] <- lm(nHouseLessTwoMin ~ D, data = prodfr)
mprod[[3]] <- lm(nBreed ~ D, data = prodfr)
mprod[[4]] <- lm(nLarvae ~ D, data = prodfr)
stargazer(mprod[[3]], mprod[[4]],
          mprod[[1]], mprod[[2]],
          se = starprep(mprod[[3]], mprod[[4]],
                        mprod[[1]], mprod[[2]],
                        se_type = "HC1"),
          dep.var.labels = c('\\shortstack{Breeding Sites \\\\ Terminated}',
                             '\\shortstack{Larvae \\\\ Terminated}',
                             '\\shortstack{Houses \\\\ Visited}',
                             '\\shortstack{Houses Visited \\\\ in Less than \\\\ Two Minutes}'),
          keep.stat = c('ser', 'n'),
          notes = c('Robust standard errors in parenthesis.'),
          keep = c('DIndividual', 'DCollective'),
          covariate.labels = c('Individual Bonus',
                               'Collective Bonus'),
          title = 'Field Productivity', header = FALSE,
          label = 'tab:productivity')
```

Teams who received collective bonuses are the most effective in finding
larvae. Subjects who worked under this treatment status have a `r round(as.numeric(coef(mprod[[4]])[3]*100),1)`% (CI: [`r round(coefci(mprod[[4]], vcov = vcovHC(mprod[[4]], type = "HC1"), level = 0.9), digits=3)[3,1]*100`%, `r round(coefci(mprod[[4]], vcov = vcovHC(mprod[[4]], type = "HC1"), level = 0.9), digits=3)[3,2]*100`%]) higher
likelihood of finding larvae than those in the control group. Locating mosquito
larvae is a difficult task, thus the probability of successfully completing the
task increases when subjects work in teams. Furthermore, our collective bonus
scheme was not excludable within the teams, thus healthcare workers had an
incentive to cooperate and receive higher rewards.

Subjects who received monetary incentives visited fewer houses than those who
did not earn financial rewards. The result is statistically significant for the
individual treatment group. While the finding seems counter-intuitive, it
actually attests the effectiveness of the treatment. This is because we offered
incentives for subjects to exterminate larvae and find breeding sites, not to
visit a greater number of households. As a result, participants in the 
treatment groups did a thorough job in each household, which explains the lower
number of visits during the allotted time. We find that subjects in the
individual and in the collective bonus groups visited `r round(as.numeric(coef(mprod[[1]])[2]), 3)` (CI: [`r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[2,1]`, `r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[2,2]`]) and `r round(as.numeric(coef(mprod[[1]])[3]), 3)` (CI: [`r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[3,2]`]) households, respectively.
